curatedMetagenomicData

### 2020-02-03 manuscript_NS_MRD.Rmd
updated

>>>>

```{r Abundance}

abundance <- function(atlas.pseq, title_text){
  pseq.ph <- aggregate_taxa(atlas.pseq, "Phylum")

pseq.ph.rel <- microbiome::transform(pseq.ph, "compositional")

plot.comp.rel <- plot_composition(pseq.ph.rel, x.label = "sample") +
theme(legend.position = "bottom") + theme_bw() +
theme(axis.text.x=element_blank()) + scale_fill_brewer(palette = "Paired") + guides(fill=guide_legend("Phylum")) + theme(legend.text = element_text( face="italic"))

p <- plot.comp.rel
 save_plot(paste(title_text,".png", sep = ""), p )

abundance.bar <- function(atlas.pseq, title_text){
  p.new <- aggregate_taxa(atlas.pseq, "Phylum")

p.new.rel <- microbiome::transform(p.new, "compositional")

plot.p.new.rel <- plot_composition(p.new.rel, average_by = "mnd", x.label = " ", plot.type = "barplot") + guides(fill=guide_legend(title="Phylum")) + theme(legend.text = element_text( face="italic")) + theme_classic()

p <- plot.p.new.rel + scale_fill_brewer(palette = "Paired")

 save_plot(paste(title_text,".png", sep = ""), p )
}

abundance(atlas.pseq, "atlas_abundance")
abundance(pseq.subset, "pseq_abundance")

abundance.bar(atlas.pseq, "atlas_bar")
abundance.bar(pseq.subset, "pseq_bar")
